Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-03 paper/paper.tex
hscc17
Signed-off-by: Alessandro Abate <aabate@Alessandros-MacBook-Pro.local>

\blue{Please insert a figure clearly distinguishing between continuous and discretised/quantised plant - a template is in a picture sent out by Lucas late last week. 
We should have 
\begin{itemize}
\item 
$G(s) = \frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}$ -- this is the physical plant, which is focus of interest and to which we refer our specifications/properties 
\item 
$G(z, T) = \frac{\bar b_{0}+\bar b_{1}z^{-1}+...+\bar b_{M_G}z^{-M_G}}{\bar a_{0}+\bar a_{1}z^{-1}+...+\bar a_{N_G}z^{-N_G}}$ -- this is the time-discretised plant (notice the notation encompasses explicitly the sample time $T$; please write out explicitly the relationship between the $a_i$ and the $\bar a_i$ and likewise for the numerator's coefficients 
(in particular, are the orders $M_G, N_G$ the same? 
\item 
we have $Y(z) = G(z,T) U(z)$; then, we introduce $\hat Y(z) \doteq Y(z) + \nu (z)$, so that 
$$
\frac{\hat Y(z)}{U(z)} = G(z,T) + \frac{\nu (z)}{U(z)} = G(z,T) + \Delta G_Q(z) \doteq \hat G(z) ,  
$$ 
where $\Delta G_Q(z)$ is an error term accounting for the quantisation effects 
\item 
finally, we encompass the errors resulting from employing finite parameters representation, 
which we encompass in a term $\Delta G_P(z)$: is this error additive, so that we would get to a 
$$
\tilde G(z) \doteq \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z)?  
$$ 
Dario, can you write it out explicitly? In other words, if 
$$
\hat G(z) = G(z,T) + \Delta G_Q(z) = \frac{\hat b_{0}+\hat b_{1}z^{-1}+...+\hat b_{M_G}z^{-M_G}}{\hat a_{0}+\hat a_{1}z^{-1}+...+\hat a_{N_G}z^{-N_G}},  
$$ 
then what is the explicit expression of 
$$
\tilde G(z) = \frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}?
$$
(Notice that the orders $M_G, N_G$ need to be properly taken care of.)
\end{itemize}
}

>>>>

\blue{Please insert a figure clearly distinguishing between continuous and discretised/quantised plant - a template is in a picture sent out by Lucas late last week. 
We should have 
\begin{itemize}
\item 
$G(s) = \frac{s^{M_G}b_{0}+s^{M_G-1}b_{1}+...+b_{M_G}}{s^{N_G}a_{0}+s^{N_G-1}a_{1}+...+a_{N_G}}$ -- this is the physical plant, which is focus of interest and to which we refer our specifications/properties 
\item 
$G(z, T) = \frac{\bar b_{0}+\bar b_{1}z^{-1}+...+\bar b_{M_G}z^{-M_G}}{\bar a_{0}+\bar a_{1}z^{-1}+...+\bar a_{N_G}z^{-N_G}}$ -- this is the time-discretised plant (notice the notation encompasses explicitly the sample time $T$; please write out explicitly the relationship between the $a_i$ and the $\bar a_i$ and likewise for the numerator's coefficients 
(in particular, are the orders $M_G, N_G$ the same? 
\item 
we have $Y(z) = G(z,T) U(z)$; then, we introduce $\hat Y(z) \doteq Y(z) + \nu (z)$, so that 
$$
\frac{\hat Y(z)}{U(z)} = G(z,T) + \frac{\nu (z)}{U(z)} = G(z,T) + \Delta G_Q(z) \doteq \hat G(z) ,  
$$ 
where $\Delta G_Q(z)$ is an error term accounting for the quantisation effects 
\item 
finally, we encompass the errors resulting from employing finite parameters representation, 
which we encompass in a term $\Delta G_P(z)$: is this error additive, so that we would get to a 
$$
\tilde G(z) \doteq \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z)?  
$$ 
Dario, can you write it out explicitly? In other words, if 
$$
\hat G(z) = G(z,T) + \Delta G_Q(z) = \frac{\hat b_{0}+\hat b_{1}z^{-1}+...+\hat b_{M_G}z^{-M_G}}{\hat a_{0}+\hat a_{1}z^{-1}+...+\hat a_{N_G}z^{-N_G}},  
$$ 
then what is the explicit expression of 
$$
\tilde G(z) = \frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}?
$$
(Notice that the orders $M_G, N_G$ need to be properly taken care of.)
\item 
Now, it's over the transfer function $\tilde G(z)$ that we want to synthesise the parameters of a template $C(z)$. 
This controller's transfer function will be subject to the same quantisation and precision limits as the plant's: 
we need to argue that the way we do synthesis affects manipulation of quantities that relate to specific errors and be explicit about these. 
\item[]
\item 
An additional source of error can be related to the fact that a plant transfer function, 
per se a physical entity, is actually represented in a program imprecisely: 
this would mean that $G(s)$ is actually 
$$
G^\ast (s) \doteq \frac{s^{M_G^\ast}b_{0}+s^{M_G^\ast-1}b_{1}+...+b_{M_G}}{s^{N_G^\ast}a_{0}+s^{N_G^\ast-1}a_{1}+...+a_{N_G}}, 
$$ 
which perhaps can indeed be re-written as $G^\ast (s) = G(s) + \Delta G_P(s)$? (This proof should come from that above.) 
We should argue that this error is encompassed by the one derived above (or isn't it?). 
\end{itemize}
}
